---
title: "Dashboard Context"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

### NYC Restaurant Inspections

The New York City Department of Health and Mental Hygiene (NYC DOHMH) conducts unannounced restaurant inspections on an annual basis in order to check for compliance with policies on food handling, food temperature, personal hygiene of restaurant workers, and vermin control. Regulation violations are each worth a number of points, which are totaled at the end of the inspection. Scores are converted into grades, where a lower score (ie. less regulation violations) earns a higher grade.

Each regulation violation falls into one of three categories:

1. **A public health hazard**: For instance, failing to store food at an appropriate temperature, results in a minimum score of 7

2. **A critical violation**: For example, improperly washing raw vegetables prior to serving, results in a minimum score of 5

3. **A general violation**: For instance, improperly sanitizing cookware, results in a minimum score of 2

Additional points can then be assigned based on the severity of the violation, ranging from 1-5, at the discretion of the inspector. For more details, refer to this [information sheet](https://www1.nyc.gov/assets/doh/downloads/pdf/rii/how-we-score-grade.pdf) developed by the NYC DOHMH.

*NYC restaurant inspection data are publicly available at [NYC Open Data](https://data.cityofnewyork.us/Health/DOHMH-New-York-City-Restaurant-Inspection-Results/43nn-pn8j) and are updated daily.*

___

### Dashboard Context

For the following flexdashboard, we'll be using a subset of NYC restaurant inspection data accessed in October 2017 and compiled into the `p8105.datasets` package for this class. This dataset contains ~400,000 rows and 26 columns, with information on restaurant name and location, type of food, inspection date, and details on violation codes, total scores, and associated grades. The data is also longitudinal in nature, with multiple rows per restaurant representing inspections over time. 

*You can find more information on how this specific raw dataset was obtained [here](https://p8105.com/dataset_restaurant_inspections.html).*

___

In this flexdashboard, we'll be looking at restaurant inspection scores and dates in the year 2016 for restaurants in NYC.

```{r Loading-in-dataset, include=FALSE}
data("rest_inspec")

rest_inspec =
  rest_inspec %>%
  select(
    camis, boro, critical_flag, cuisine_description, inspection_date, inspection_type, score, grade) %>%
  mutate(year = lubridate::year(inspection_date),
         month = lubridate::month(inspection_date, label = TRUE, abbr = FALSE),
         day = lubridate::day(inspection_date),
         cuisine_description = recode(cuisine_description, "Latin (Cuban, Dominican, Puerto Rican, South & Central American)" = "Latin", "Café/Coffee/Tea" = "Cafe", "Bottled beverages, including water, sodas, juices, etc." = "Bottled Beverages", "Juice, Smoothies, Fruit Salads" = "Juice and Smoothies")) %>%
  filter(
    score >= 0,
    inspection_type == "Cycle Inspection / Re-inspection",
    grade != "Not Yet Graded",
    grade != "Z",
    cuisine_description != "Not Listed/Not Applicable",
    critical_flag != "Not Applicable",
    inspection_date >= "2016-01-01",
    inspection_date <= "2016-12-31"
  ) %>%
  drop_na()
```

There are `r nrow(rest_inspec)` restaurant inspection observations in the subsetted dataset we'll be using for the Flexdashboard, with "Cycle Re-inspection" data from `r rest_inspec %>% pull(camis) %>% n_distinct()` unique restaurants in NYC throughout 2016.

*For more information on how this dataset was cleaned and coded to use in the Flexdashboard, see the `flexdashboard` file in my [GitHub repository](https://github.com/sophyee/sophyee.github.io.git).*

___

### Let's Explore!

Click on the `Dashboard` tab at the top of this page to open up an interactive dashboard.

```{r boxplot, include=FALSE}
rest_inspec %>%
  mutate(
    score_label = str_c("Score: ", score),
    boro = fct_reorder(boro, score)
  ) %>%
  plot_ly(
    x = ~boro, y = ~score, color = ~boro,
    type = "box", mode = "markers", colors = "viridis",
    alpha = 0.3, text = ~score_label) %>%
    layout(title = 'Restaurant Inspection Score Distributions in 2016, by Borough', 
    xaxis = list(title = "Borough"), yaxis = list(title = "Inspection Score"))
```

```{r barchart, include=FALSE}
rest_inspec %>%
  group_by(cuisine_description) %>%
  summarise(cuisine_type = mean(score),
            avg_score_label = str_c("Average Score: ", cuisine_type)) %>%
  mutate(cuisine_description = fct_reorder(cuisine_description, cuisine_type)) %>%
  plot_ly(
    x = ~cuisine_description, y = ~cuisine_type,
    type = "bar", mode = "markers", colors = "viridis",
    alpha = 0.5, text = ~avg_score_label)  %>%
    layout(title = 'Average NYC Restaurant Inspection Score by Cuisine Type in 2016', 
    xaxis = list(title = "Cuisine Type"), yaxis = list(title = "Avg Inspection Score"))
```

```{r violinplot, include=FALSE}
rest_inspec %>%
  mutate(
    score_label = str_c("Score: ", score),
    boro = fct_reorder(boro, score)
  ) %>%
  plot_ly(
    x = ~boro, y = ~score, color = ~grade,
    type = "violin", colors = "viridis",
    alpha = 0.3, text = ~score_label) %>%
    layout(title = 'Restaurant Inspection Score Distributions in 2016, by Borough and Grade', 
    xaxis = list(title = "Borough"), yaxis = list(title = "Inspection Score"), legend = list(title = list(text = "<b> Inspection Grade </b>")))
  
```


